Exit Strategy

### 2015-11-14 manuscript.tex
Quite

\pagestyle{fancy}
\fancyhead{}
\lhead{Chesnais, Pourchet, Vogan}
\chead{Exit Strategy}
\rhead{\today}
\fancyfoot{}
\rfoot{\thepage}
\lfoot{\includegraphics[height=20pt]{http://paul.chesnais.com/assets/favicon.png}}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}

\usepackage{listings, color, times, textcomp, float, hyperref, setspace, subcaption}
\definecolor{Code}{rgb}{0,0,0}
\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
\definecolor{Numbers}{rgb}{0.5,0,0}
\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
\definecolor{Keywords}{rgb}{0,0,1}
\definecolor{self}{rgb}{0,0,0}
\definecolor{Strings}{rgb}{0,0.63,0}
\definecolor{Comments}{rgb}{0,0.63,1}
\definecolor{Backquotes}{rgb}{0,0,0}
\definecolor{Classname}{rgb}{0,0,0}
\definecolor{FunctionName}{rgb}{0,0,0}
\definecolor{Operators}{rgb}{0,0,0}
\definecolor{Background}{rgb}{0.98,0.98,0.98}

\lstset{numbers=left,numberstyle=\footnotesize,numbersep=1em,xleftmargin=1em,
framextopmargin=2em,framexbottommargin=2em,showspaces=false,showtabs=false,
showstringspaces=false,frame=l,tabsize=4,basicstyle=\ttfamily\small\setstretch{1},
backgroundcolor=\color{Background},language=Python,
commentstyle=\color{Comments}\slshape,stringstyle=\color{Strings},
morecomment=[s][\color{Strings}]{"""}{"""},
morecomment=[s][\color{Strings}]{'''}{'''},morekeywords={import,from,class,def,
for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,
None,access,as,del,except,exec,finally,global,import,lambda,pass,print,raise,try,
assert},keywordstyle={\color{Keywords}\bfseries},morekeywords={[2]@invariant},
keywordstyle={[2]\color{Decorators}\slshape},emph={self},
emphstyle={\color{self}\slshape},breaklines=true}

@@

\href{http://paul.chesnais.com/assets/favicon.png}{blop}

>>>>

\pagestyle{fancy}
\fancyhead{}
\lhead{Chesnais, Pourchet, Vogan}
\chead{Exit Strategy}
\rhead{\today}
\fancyfoot{}
\rfoot{\thepage}
\lfoot{\includegraphics[height=20pt]{Logo}}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}

\usepackage{listings, color, times, textcomp, float, hyperref, setspace, subcaption}
\definecolor{Code}{rgb}{0,0,0}
\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
\definecolor{Numbers}{rgb}{0.5,0,0}
\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
\definecolor{Keywords}{rgb}{0,0,1}
\definecolor{self}{rgb}{0,0,0}
\definecolor{Strings}{rgb}{0,0.63,0}
\definecolor{Comments}{rgb}{0,0.63,1}
\definecolor{Backquotes}{rgb}{0,0,0}
\definecolor{Classname}{rgb}{0,0,0}
\definecolor{FunctionName}{rgb}{0,0,0}
\definecolor{Operators}{rgb}{0,0,0}
\definecolor{Background}{rgb}{0.98,0.98,0.98}
\definecolor{mygreen}{RGB}{28,172,0}
\definecolor{mylilas}{RGB}{170,55,241}

\lstdefinestyle{Python}{
  backgroundcolor=\color{Background},basicstyle=\ttfamily\small\setstretch{1},breaklines=true,
  commentstyle=\color{Comments}\slshape,emph={self},emphstyle={\color{self}\slshape},frame=l,framexbottommargin=2em,
  framextopmargin=2em,keywordstyle={[2]\color{Decorators}\slshape},keywordstyle={\color{Keywords}\bfseries},
  language=Python,morecomment=[s][\color{Strings}]{"""}{"""},morecomment=[s][\color{Strings}]{'''}{'''},
  morekeywords={[2]@invariant},morekeywords={import,from,class,def,for,while,if,is,in,elif,else,not,and,or,print,break,
  continue,return,True,False,None,access,as,del,except,exec,finally,global,import,lambda,pass,print,raise,try,assert},
  numbers=left,numbersep=1em,numberstyle=\footnotesize,showspaces=false,showstringspaces=false,showtabs=false,
  stringstyle=\color{Strings},tabsize=4,xleftmargin=1em,
}

\lstdefinestyle{Matlab}{
  backgroundcolor=\color{Background},basicstyle=\ttfamily\small\setstretch{1},breaklines=true,
  commentstyle=\color{mygreen},emph=[1]{for,end,break},emphstyle=[1]\color{red},frame=l,identifierstyle=\color{black},
  keywordstyle=[2]{\color{black}},keywordstyle=\color{blue},language=Matlab,literate={~} {\texttildelow}{1},
  morekeywords=[2]{1},morekeywords={matlab2tikz},numbers=left,numbersep=9pt,numberstyle={\tiny \color{black}},
  showstringspaces=false,stringstyle=\color{mylilas},
}

@@

\section{Abstract}
\label{sec:abstract}

\section{Executive Summary}
\label{sec:executive_summary}

% Antoine's stuff and thing
\section{Deterministic Model}
\label{sec:deterministic_model}

% Paul's stuff and things
\section{Stochastic Model}
\label{sec:stochastic_model}
